Plots_Genome

### 2024-05-28 Code/Plots_Genome.Rmd
Update Plots_Genome.Rmd

```{r, assign filepaths, include = FALSE}
DataIn <- file.path("..","Data", "CleanData")
Figures <- file.path("..", "Output", "Figures")
PLOSFiguresRoundX <- file.path("..", "Output", "PLOSFiguresRound1")
# BLAST <- file.path("..", "BLAST")
```

@@

```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
# ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
# ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms_julie.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
```

@@

DNARepairTab <- DNARepair %>% 
  mutate(EnzymeName = case_when(EC == "3.2.2.21" ~ "DNA-3-methyladenine glycosylase II",
                                EC == "3.1.22.4" ~ "crossover junction endodeoxyribonuclease",
                                EC == "3.1.11.6" ~ "exodeoxyribonuclease VII",
                                EC == "3.2.2.21" ~ "DNA-3-methyladenine glycosylase II",
                                EC == "3.1.3.18" ~ "phosphoglycolate phosphatase",
                                EC == "3.2.2.23" ~ "DNA-formamidopyrimidine glycosylase",
                                EC == "3.1.11.2" ~ "exodeoxyribonuclease III",
                                EC == "4.2.99.18" ~ "DNA-(apurinic or apyrimidinic site) lyase",
                                EC == "3.2.2.27" ~ "uracil-DNA glycosylase",
                                EC == "3.1.11.5" ~ "exodeoxyribonuclease V",
                                EC == "6.5.1.2" ~ "DNA ligase (NAD+)",
                                EC == "4.1.99.3" ~ "deoxyribodipyrimidine photolyase",
                                EC == "6.5.1.1" ~ "DNA ligase (ATP)",
                                EC == "2.7.7.7" ~ "DNA-directed DNA polymerase")) %>% 
  mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
                                 Strain == "CCMP1986" ~ "MED4",
                                 Strain == "MIT9313" ~ "MIT9313",
                                 Strain == "NATL2A" ~ "NATL2A")) %>%
  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313")))

DNARepairFig <- DNARepairTab %>% 
  ggplot() +
  geom_point(aes(x = fct_reorder(EnzymeName, desc(Gene_count)), y = StrainLabel, size = (Gene_count))) + #y = interaction(Genus, species, StrainLabel, sep = " ")
  # facet_grid(rows = vars(Genus), scales = "free", space = "free") +
  # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  scale_x_discrete(position = "bottom") +
  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 1, angle = 80)  +
  labs(x = "Enzyme name",
       #y = "Organism",
       color = "Gene count",
       size = "Gene count") +
  facet_grid(rows = vars(StrainLabel), scale = "free") +
   theme(axis.text = element_text(size = 7, color = "black"),
         legend.position = "right",
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         axis.title.x = element_text(vjust=5),
        axis.ticks.y = element_blank(),
  # axis.title = element_text(size = 40, color = "black"),
  #        title = element_text(size = 30),
  #     # axis.text.x = element_text(size = 30, color = "black"),
  #       axis.text.y = element_text(size = 30, color = "black"),
        strip.text = element_text(size = 6),
        legend.box.background = element_rect(colour = "black")
  #       # legend.key.size = unit(10, 'cm'), #change legend key size
  #       # legend.key.height = unit(2, 'cm'), #change legend key height
  #       # legend.key.width = unit(1, 'cm'), #change legend key width
  #       legend.title =  element_text(size = 30),  #change legend title font size
  #       legend.text = element_text(size = 30))   #change legend text font size
  )

>>>>

```{r, assign filepaths, include = FALSE}
DataIn <- file.path("..","Data", "CleanData")
Figures <- file.path("..", "Output", "Figures")
PLOSFiguresRoundX <- file.path("..", "Output", "PLOSRound2")
# BLAST <- file.path("..", "BLAST")
```

@@

```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
# ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms_julie.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 17)
```

@@

DNARepairTab <- DNARepair %>% 
  mutate(EnzymeName = case_when(EC == "3.2.2.21" ~ "DNA-3-methyladenine glycosylase II",
                                EC == "3.1.22.4" ~ "crossover junction endodeoxyribonuclease",
                                EC == "3.1.11.6" ~ "exodeoxyribonuclease VII",
                                EC == "3.2.2.21" ~ "DNA-3-methyladenine glycosylase II",
                                # EC == "3.1.3.18" ~ "phosphoglycolate phosphatase",
                                EC == "3.2.2.23" ~ "DNA-formamidopyrimidine glycosylase",
                                EC == "3.1.11.2" ~ "exodeoxyribonuclease III",
                                EC == "4.2.99.18" ~ "DNA-(apurinic or apyrimidinic site) lyase",
                                EC == "3.2.2.27" ~ "uracil-DNA glycosylase",
                                EC == "3.1.11.5" ~ "exodeoxyribonuclease V",
                                EC == "6.5.1.2" ~ "DNA ligase (NAD+)",
                                EC == "4.1.99.3" ~ "deoxyribodipyrimidine photolyase",
                                EC == "6.5.1.1" ~ "DNA ligase (ATP)",
                                EC == "2.7.7.7" ~ "DNA-directed DNA polymerase")) %>% 
  mutate(StrainLabel = case_when(Strain == "CCMP1375" ~ "SS120",
                                 Strain == "CCMP1986" ~ "MED4",
                                 Strain == "MIT9313" ~ "MIT9313",
                                 Strain == "NATL2A" ~ "NATL2A")) %>%
  mutate(StrainLabel = factor(StrainLabel, levels = c("MED4", "NATL2A", "SS120", "MIT9313")))

DNARepairFig <- DNARepairTab %>% 
  filter(EC != "3.1.3.18") %>% #PGP is not truly a DNA repair enzyme. 
  ggplot() +
  geom_point(aes(x = fct_reorder(EnzymeName, desc(Gene_count)), y = StrainLabel, size = (Gene_count))) + #y = interaction(Genus, species, StrainLabel, sep = " ")
  # facet_grid(rows = vars(Genus), scales = "free", space = "free") +
  # scale_color_gradient(low = "#0980F6", high = "#F67F09", na.value = "black") +
  scale_x_discrete(position = "bottom") +
  scale_radius(breaks = c(1,2,3,4,5), range = c(1,4)) +
  theme_bw() +
  ggpubr::rotate_x_text(hjust = 1, angle = 80)  +
  labs(x = "Enzyme name",
       #y = "Organism",
       color = "Gene count",
       size = "Gene count") +
  facet_grid(rows = vars(StrainLabel), scale = "free") +
   theme(axis.text = element_text(size = 7, color = "black"),
         legend.position = "right",
         axis.text.y = element_blank(),
         axis.title.y = element_blank(),
         axis.title.x = element_text(vjust=5),
        axis.ticks.y = element_blank(),
  # axis.title = element_text(size = 40, color = "black"),
  #        title = element_text(size = 30),
  #     # axis.text.x = element_text(size = 30, color = "black"),
  #       axis.text.y = element_text(size = 30, color = "black"),
        strip.text = element_text(size = 6),
        legend.box.background = element_rect(colour = "black")
  #       # legend.key.size = unit(10, 'cm'), #change legend key size
  #       # legend.key.height = unit(2, 'cm'), #change legend key height
  #       # legend.key.width = unit(1, 'cm'), #change legend key width
  #       legend.title =  element_text(size = 30),  #change legend title font size
  #       legend.text = element_text(size = 30))   #change legend text font size
  )
